The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
text for yearly interactions

%%%%%%%%%%%%%%%%
The regression coefficients for the categorical variables year and GI region, and their interaction under each of the four models are depcited in \ref{fig:violin}. The coefficients for the continuous variables are summarised in Table \ref{tab:contvar}.
In terms of magnitude, GI region has the highest possible absolute value for each model. The most notable

\begin{figure}
  \includegraphics{violinplot.pdf}
  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}
  \end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%
The regression coefficients for the categorical variables year and GI region, and their interaction under each of the four models are depicted in \ref{fig:yearly}. The first year for a model's data is used as the baseline. The Adelaide Hills is used as the regional baseline with the interaction between year and region using the first year and the Adelaide Hills as the baseline. Region and year contributed, in some but not all cases, more than the other variables. However, some years are not significant, as they are not statistically different from 0, given their error. Models 4 and 5 appear very similar, however this is likely due to the averaging generalising the finer differences between specific year and region combinations. No trend is apparent for any model, with only a slight drop for 2019 in Models 1 and 2, and a slight increase after 2018 for Models 3, 4 and 5.

\begin{figure}
  \includegraphics{yearly_plots.pdf}
  \caption{Model Coefficient values for GI Region and Year, with standard error bars. The average of Models 2, 4 and 5 were used in place of every combination of region and year.}\label{fig:yearly}
  \end{figure}

@@

%Interestingly all but Model 2 do not appear to capture the introduction of Tariffs to Australian exports, which had a pronounced effect within the sale and production of wine in Australia . This needs a wine aus ref and to be put in the discussion
